---
title: 'Group Project: 2020-2021 Student Loan Analysis'
author: "Group BD2"
date: "2023-02-28"
output: html_document
---

```{r message = FALSE}
library(tidyverse)
student_loans <- read_delim("data/Student Loan Debt by School 2020-2021.csv")
```

# Project Set-up (Data Analysis)
```{r, echo=FALSE}
# Dimensions & Column Names $ Sample 

dim(student_loans)
colnames(student_loans)
student_loans %>% 
  sample_n(10)

```
```{r echo=FALSE}
# Checking NAs

student_loans %>% 
  filter(is.na(City)) %>% 
  head(10)

student_loans %>%
  filter(is.na(State)) %>% 
  head(10) 

student_loans %>% 
  filter(is.na(School)) %>% 
  head(10)
```



### 1. Compute Average Loans per State. Possible top 10 (Mike)

```{r}
# Multiple terms for how loans were carried out. Here, I chose disbursement. 

student_loans %>% 
  filter( !is.na(`$ of Disbursements`),
         !is.na(State),
         `Loan Type` != "Total") %>% 
  group_by(State) %>% 
  summarize(avg_loan_state = mean(`$ of Disbursements`)) %>% 
  mutate(rank = rank(desc(avg_loan_state))) %>% 
  arrange(rank) %>% 
  head(10)
```

```{r}
# Double Checking Numbers

student_loans %>% 
  filter(State == "DC", 
         !is.na(`$ of Disbursements`),
         `Loan Type` != "Total") %>% 
  group_by(State) %>% 
  summarize(avg_loan = mean(`$ of Disbursements`)) %>% 
  print()
```

Numbers look good. Sorted from rank 1 to 50. 4 Additional states
included (Puerto Rico, DC, and so forth.)


### 2. Compute top 10 average loans by city. Organize city school loans by state (Nick)



### 3. Organize and arrange highest to lowest loan types taken out (Nathaniel)



### 4. Compute average number of recipients who received a loan per college. (Megan)



### 5. Categorize public and private schools with their average loans taken out. (Everyone)

